### 2017-09-10 paper/evaluation.tex
pass on evaluation

%% \Jbc{Issues do Maven: (1) Report de contagem de testes, (2) crash de
%% jvm - maven surefire nao tratava algumas exceptions que aconteciam na
%% execucao do teste, (3) timeout}
%% The script we implemented to measure time and flakiness takes a list
%% of tests classes to run as input and outputs the results (\ie, number
%% of test methods, failures, skips, and elapsed time) for each parallel
%% configuration.
%%\Comment{ To obtain parallel configurations, we implemented a script
%%  that takes a subject and a configuration label as inputs (\eg
%%  \CodeIn{mapdb "c0"}), and the script outputs the modified version of
%%  the subject with the desired configuration. The workflow consists in
%%  copying the project directory to a new directory, finding all
%%  existing build files (\ie, \pomf{} files), and modifying all
%%  existing Maven Surefire configurations with new values for the
%%  parameters \CodeIn{parallel}, \CodeIn{forkCount}, and
%%  \CodeIn{threadCount} using an XPath~\cite{xpath} library to
%%  manipulate XML documents. For configurations with forked JVMs
%%  enabled (\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
%%  \CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per
%%  core).  To adjust the pool of threads for parallelism within a JVM,
%%  we changed the parameter \CodeIn{threadCount} with \Jbc{should we
%%    consider 2 as it is the number of native threads per core OR 6 as
%%    it represents 3 Cores * 2 native threads?}.To run the subjects and
%%  their respective variations (\ie, the modified versions according to
%%  the parallelism configuration), we used a similar approach as
%%  described in Figure~\ref{fig:mvn-execution} except that...  }
%% For efficiency, we reported the speedup (\ie, $T_{\text{s}} /
%% T_{\text{p}}$), and for flakiness, we reported the rate of failing
%% tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).
\Jbc{Falta atualizar essa discussao....
Table~\ref{tab:rq6-table} summarizes results ordered by subject's
name. Recall that we only executed one module for each subject.
Values are averaged across multiple executions.  We did not report
standard deviations as they are very small in all cases.  Considering
flakiness, results show that 0\% of flakiness have been reported in 26
of the 60 combinations analyzed (43\% of the total) and that for seven
of the ten projects 0\% flakiness was reported in at least one of the
configurations.  The projects with flakiness in all configurations
were \CodeIn{AWS SDK}, \CodeIn{GoogleCloud}, and \CodeIn{Moquette}.
It is worth highlighting the unfortunate case of \CodeIn{Moquette},
which manifested more than 20\% flaky tests in every configuration.
Considering time, it is noticeable from the averages, perhaps as
expected, an increasing speedup from configuration
\emph{\SeqClassParMeth} to \emph{\ParClassParMeth} and from
configuration \emph{\ForkSeq} to \emph{\ForkParMeth}.  It is also
worth mentioning that some combinations manifested slowdown instead of
speedup.  Recall that parallel execution introduces the overhead of
spawning and managing JVMs and threads.
}

\begin{center}
\fbox{
\begin{minipage}{8cm}
\textit{Answering \numRQIssuesOne{}:~Overall results indicate that the
  test suites of 70\% of the projects we analyzed could be run in
  parallel without manifesting any flaky tests.  In some of these
  cases, speedups were significant, ranging from 1x to 28.8x.}
\end{minipage}
}
\end{center}

@@

%%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th
%%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile FC
%%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
%%  LocalWords:  outliers apache uber chaperone facebookarchive AWS
%%  LocalWords:  linkbench priori SDK GoogleCloud Moquette JVMs dir
%%  LocalWords:  xml basicstyle boxpos numberstyle deletekeywords JVM
%%  LocalWords:  uncompilable leftmargin quartile DskipTests forkMode
%%  LocalWords:  threadCount forkCount lrr BounceStorage Flink Gerrit
%%  LocalWords:  JenkinsCI Spotify Javaslang Jcabi Github Hazelcast
%%  LocalWords:  Jankotek MapDB Dparallel classesAndMethods Mapstruct
%%  LocalWords:  DataflowJavaSDK modularized JUnit llrrr lightgray rr
%%  LocalWords:  GitHub amongst Xeon runtime Scalability Dataflow sdk
%%  LocalWords:  JCTools RipMe classpath ParallelComputer livelock io
%%  LocalWords:  mapdb workflow XPath boxplot llcr javaslang jcabi
%%  LocalWords:  github hazelcast jankotek OpenNLP yegor Rultor vavr
%%  LocalWords:  Vavr SNE Urbanairship Datacube

>>>>

%% \Jbc{Issues do Maven: (1) Report de contagem de testes, (2) crash de
%% jvm - maven surefire nao tratava algumas exceptions que aconteciam na
%% execucao do teste, (3) timeout}
%% The script we implemented to measure time and flakiness takes a list
%% of tests classes to run as input and outputs the results (\ie, number
%% of test methods, failures, skips, and elapsed time) for each parallel
%% configuration.
%%\Comment{ To obtain parallel configurations, we implemented a script
%%  that takes a subject and a configuration label as inputs (\eg
%%  \CodeIn{mapdb "c0"}), and the script outputs the modified version of
%%  the subject with the desired configuration. The workflow consists in
%%  copying the project directory to a new directory, finding all
%%  existing build files (\ie, \pomf{} files), and modifying all
%%  existing Maven Surefire configurations with new values for the
%%  parameters \CodeIn{parallel}, \CodeIn{forkCount}, and
%%  \CodeIn{threadCount} using an XPath~\cite{xpath} library to
%%  manipulate XML documents. For configurations with forked JVMs
%%  enabled (\ie, \ForkSeq{} and \ForkParMeth{}), we changed the
%%  \CodeIn{forkCount} with the value \CodeIn{1C} (\ie, one JVM per
%%  core).  To adjust the pool of threads for parallelism within a JVM,
%%  we changed the parameter \CodeIn{threadCount} with \Jbc{should we
%%    consider 2 as it is the number of native threads per core OR 6 as
%%    it represents 3 Cores * 2 native threads?}.To run the subjects and
%%  their respective variations (\ie, the modified versions according to
%%  the parallelism configuration), we used a similar approach as
%%  described in Figure~\ref{fig:mvn-execution} except that...  }
%% For efficiency, we reported the speedup (\ie, $T_{\text{s}} /
%% T_{\text{p}}$), and for flakiness, we reported the rate of failing
%% tests (\ie, $\mathit{\%_\text{fail} = failures / tests}$).

\sloppy Table~\ref{tab:rq6-table} summarizes results ordered by
subject's name.  Values are averaged across multiple executions.  We
did not report standard deviations as they are very small in all
cases.  As to identify the potential causes of flakiness, we inspected
the exceptions reported in execution logs. We found that, in most
of the cases, flakiness was caused by race conditions: approximately
97.5\% of the failures were caused by a \CodeInF{null} dereference and 1.6\% were
caused by concurrent access on unsynchronized data structures.\Comment{
  More precisely, the manifested exceptions were
  \CodeInF{ConcurrentModificationException} (0.8\%),
  \CodeInF{NoSuchElementException} (0.7\%), and
  \CodeInF{ArrayIndexOutOfBoundsException} (0.7\%).}  Cases of likely
broken test dependencies were not as prevalent as race conditions
(0.8\% of the total): \CodeInF{EOFException} (0.2\%),
\CodeInF{FileSystemAlreadyExistsException} (0.2\%), and
\CodeInF{BufferOverflowException} (0.4\%). Results suggest that
anticipating race conditions to schedule test executions would have
higher impact compared to breaking test dependencies using a tool such
as TestElectric~\cite{bell-etal-esecfse2015}.

The projects with flakiness
in all configurations were \CodeIn{AWS SDK}, \CodeIn{GoogleCloud}, and
\CodeIn{Moquette}.  It is worth highlighting the unfortunate case of
\CodeIn{Moquette}, which manifested more than 20\% flaky tests in
every configuration.  Considering time, it is noticeable from the
averages, perhaps as expected, an increasing speedup from
configuration \emph{\SeqClassParMeth} to \emph{\ParClassParMeth} and
from configuration \emph{\ForkSeq} to \emph{\ForkParMeth}.  It is also
worth mentioning that some combinations manifested slowdown instead of
speedup.  Recall that parallel execution introduces the overhead of
spawning and managing JVMs and threads.  Overall, results show that
0\% of flakiness have been reported in 30 of the 75 (=5x15)
pairs of project and configuration we analyzed (40\% of the total).
In for 4 of the 15 projects flakiness was not manifested in 
any combination pairs.  We noticed with some surprise that the average speedup of
configuration \emph{\SeqClassParMeth} was higher compared to
\emph{\ForkParMeth} indicating that it is not always the case that
using more CPUs pays off. Important to note that the cost of spawning
new JVMs can be significant in \emph{\ForkParMeth}.

\begin{center}
\fbox{
\begin{minipage}{8cm}
\textit{Answering \numRQIssuesOne{}:~Overall results indicate that the
  test suites of 73.33\% of the projects we analyzed could be run in
  parallel without manifesting any flaky tests.  In some of these
  cases, speedups were significant, ranging from 1x to 28.8x.}
\end{minipage}
}
\end{center}

@@

%%  LocalWords:  RQ occurence parallelization Tradeoffs API readme th
%%  LocalWords:  mvn clearcut escapeinside xleftmargin untestable LTS
%%  LocalWords:  framexleftmargin CPUs Tahr sysstat gh Vagrantfile FC
%%  LocalWords:  javadoc isolcpus JUnit's JUnitCore Gligoric boxplots
%%  LocalWords:  outliers apache uber chaperone facebookarchive AWS
%%  LocalWords:  linkbench priori SDK GoogleCloud Moquette JVMs dir
%%  LocalWords:  xml basicstyle boxpos numberstyle deletekeywords JVM
%%  LocalWords:  uncompilable leftmargin quartile DskipTests forkMode
%%  LocalWords:  threadCount forkCount lrr BounceStorage Flink Gerrit
%%  LocalWords:  JenkinsCI Spotify Javaslang Jcabi Github Hazelcast
%%  LocalWords:  Jankotek MapDB Dparallel classesAndMethods Mapstruct
%%  LocalWords:  DataflowJavaSDK modularized JUnit llrrr lightgray rr
%%  LocalWords:  GitHub amongst Xeon runtime Scalability Dataflow sdk
%%  LocalWords:  JCTools RipMe classpath ParallelComputer livelock io
%%  LocalWords:  mapdb workflow XPath boxplot llcr javaslang jcabi
%%  LocalWords:  github hazelcast jankotek OpenNLP yegor Rultor vavr
%%  LocalWords:  Vavr SNE Urbanairship Datacube dereference
%%  LocalWords:  unsynchronized ConcurrentModificationException
%%  LocalWords:  NoSuchElementException EOFException TestElectric
%%  LocalWords:  ArrayIndexOutOfBoundsException
%%  LocalWords:  FileSystemAlreadyExistsException
%%  LocalWords:  BufferOverflowException
